Regular singular Volterra equations on complex domains

### 2023-08-16 reg-sing-volterra.tex
Draft partial fraction version of cond:sing argument for level 1 example

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\kerwhole}{k}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}

@@

We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
\begin{brainstorm}
\item Kihyun Kim and his visitor (possibly Prof. Soonsik Kwon or Sung-Jin Oh)
\item Angeliki Menegaki
\end{brainstorm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}\label{sec:fn-space-defs}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}.

@@

\begin{proof}
Proposition~\ref{prop:better-proto-estimate} implies that for some constant $M$,
\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
whenever $\rho \le \tau + \min\{\epsilon, 1\}$. Theorem~\ref{thm:general_volterra} implies that our equation has a unique solution in
\[ M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
as long as $\rho \in (\tau, \tau + \gamma]$. Putting these facts together, we get the desired result.
\end{proof}

@@

\begin{align*}
    -\frac{q}{p(a)}&=-\frac{\textcolor{magenta}{q(\alpha)}+c_1(\zeta\textcolor{magenta}{'}-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
\end{align*}
hence setting $\tau_\alpha:=\frac{q(\alpha)}{p'(\alpha)}\neq 0$, we find

\begin{equation*}
    -\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
\end{equation*}
is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.

>>>>

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\kerwhole}{k}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}
\newcommand{\roots}{\mathfrak{B}}

@@

We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
\begin{brainstorm}
\item Kihyun Kim and his visitor (possibly Prof. Soonsik Kwon or Sung-Jin Oh)
\item Angeliki Menegaki
\end{brainstorm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^{\infty}$ spaces}\label{sec:fn-space-defs}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}.

@@

\begin{proof}
Propositions \ref{prop:asymptotic at infinity} and \ref{prop:better-proto-estimate} imply that for some constant $M$,
\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
whenever $\rho \le \tau + \min\{\epsilon, 1\}$. Theorem~\ref{thm:general_volterra} implies that our equation has a unique solution in
\[ M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
as long as $\rho \in (\tau, \tau + \gamma]$. Putting these facts together, we get the desired result.
\end{proof}

@@

\begin{align*}
    -\frac{q}{p(a)}&=-\frac{\textcolor{magenta}{q(\alpha)}+c_1(\zeta\textcolor{magenta}{'}-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
\end{align*}
hence setting $\tau_\alpha:=\textcolor{magenta}{-}\frac{q}{p'}\textcolor{orange}{\big|_{\zeta = \alpha}}\neq 0$, we find

\begin{equation*}
    -\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
\end{equation*}
is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.
\par\color{SkyBlue}
Since $p$ has only simple roots, the partial fraction decomposition of $1/p$ is
\[ \sum_{\beta = \roots} \left.\frac{1}{p'}\right|_{\zeta = \beta} \frac{1}{\zeta - \beta}, \]
where $\roots$ is the set containing the values of $\zeta$ at the roots of $p$.
\par\color{DarkTurquoise}
\textcolor{orange}{Nicer formulation; note different definition of $\roots$:}\par
Since $P(-\zeta)$ has only simple roots, the partial fraction decomposition of $1/P(-\zeta)$ is
\[ \sum_{-\beta = \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. It follows that
\begin{align*}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta = \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
& \in \sum_{-\beta = \roots} \frac{Q(-\alpha) + O\big(|\zeta(a') - \alpha|\big)}{P'(-\beta)\,(\zeta - \beta)} \\
%%& \in \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\alpha)\,(\zeta - \alpha)} + \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\beta)\,(\zeta - \beta)} \\
& \subset \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} + O\big(1\big)
\end{align*}
at $(\zeta(a), \zeta(a')) = (\alpha, \alpha)$. In other words, for $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, the difference
\[ -\frac{Q(-\zeta(a'))}{P(-\zeta(a))} - \frac{\tau_\alpha}{\zeta - \alpha} \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$, showing that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:sing}.

\begin{verify}
A kind of klunky way to do the Ahlfors exercise:
\begin{align*}
\frac{1}{p} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
-\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
p'\big|_{\zeta = \alpha} & = \left.\left(\frac{p}{\zeta - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
\end{align*}
\end{verify}
\color{black}
